Minicaml, a purely functional, didactical programming language with an interactive REPL.

### 2019-12-23 paper/paper.tex
optimizer optimizations >:)

\section{AST Optimization}

@@

\section{Tests}

>>>>

\section{AST Optimization}
Before being evaluated, AST expressions are analyzed and optimized by an
optimizer function that is recursively called over the tree that is representing
the expression. To achieve minimization to an unreducible (not optimizable)
form, optimizer calls are iterated on each previous call's result; this way,
when a tree representing an expression cannot be optimized again.
This is the process represented in pseudo-code:

@@

\section{Tests}
Unit testing is extensively performed using the alcotest testing framework.
